New Bayes covariant coupling methods to cope with change of priors in one-vs-one classification

### 2025-07-15 intro.tex
Addressing Peters' review

We formulate the underlying principles of one-vs-one probabilistic classification in Section 2. In Section 3 we present  different classes of coupling methods. We pay special focus to methods that commute with change of priors -- Bayes covariant methods, since such methods provide an unexpected, and elegant solution to our problem. We introduce new coupling methods by forming weighted ensembles, which we prove are also Bayes covariant when a normalizing condition on weights hold (Proposition \ref{prop:ensemble}).  In Section 4 we summarize our methodology. The results of our experiments are described in Section 5. In Section 6 we summarize our findings, provide practical guidance and outline future research directions.

>>>>

We formulate the underlying principles of one-vs-one probabilistic classification in Section 2. In Section 3 we present  different classes of coupling methods. 
We pay special attention to methods that commute with change of priors -- Bayes covariant methods, 
since such methods provide an unexpected, and elegant solution to our problem. 
We introduce new coupling methods by forming weighted ensembles. We prove such ensemble of Bayes covariant methods is again Bayes covariant
when a normalizing condition on weights hold (Proposition \ref{prop:ensemble}).  
Our experiments are described in Section 4. In Section 5 we summarize our findings, 
provide practical guidance and outline future research directions.
